@node Locale
@chapter Locale (@file{locale.h})

A @dfn{locale} is the name for a collection of parameters (affecting
collating sequences and formatting conventions) that may be different
depending on location or culture.  The @code{"C"} locale is the only
one defined in the ANSI C standard (@code{``''} is also defined;
it represents the default locale for an implementation, which in this
case is always @code{``C''}).

This is a minimal implementation, by default supporting only the required @code{``C''}
value for locale; strings representing other locales are not
honored unless the library is configured with the --enable-newlib-mb option.
When the option is specified, the added locale names: @code{"C-SJIS"}, @code{"C-JIS"},
and @code{"C-EUCJP"} may be specified for the category @code{LC_CTYPE}.  Specifying
these additional locale names for a different category results in failure.
If the multibyte locales are specified for category @code{LC_CTYPE}, this affects
the stdlib multibyte functions, the treatment of format strings for formatted
I/O, and the value of @code{mb_cur_max} which
is specified in @file{stdlib.h}.  It should be noted that the behaviors of
the character functions in @file{ctype.h} are not changed by the multibyte
locales and they continue to function as they do under the @code{"C"} locale.
 
@file{locale.h} defines the structure @code{lconv} to collect the
information on a locale, with the following fields:

@table @code
@item char *decimal_point
The decimal point character used to format ``ordinary'' numbers (all
numbers except those referring to amounts of money).  @code{``.''} in the
C locale. 

@item char *thousands_sep
The character (if any) used to separate groups of digits, when
formatting ordinary numbers.
@code{``''} in the C locale.

@item char *grouping
Specifications for how many digits to group (if any grouping is done at
all) when formatting ordinary numbers.  The @emph{numeric value} of each
character in the string represents the number of digits for the next
group, and a value of @code{0} (that is, the string's trailing
@code{NULL}) means to continue grouping digits using the last value
specified.  Use @code{CHAR_MAX} to indicate that no further grouping is
desired.  @code{``''} in the C locale. 

@item char *int_curr_symbol
The international currency symbol (first three characters), if any, and
the character used to separate it from numbers.
@code{``''} in the C locale.

@item char *currency_symbol
The local currency symbol, if any.
@code{``''} in the C locale.

@item char *mon_decimal_point
The symbol used to delimit fractions in amounts of money.
@code{``''} in the C locale.

@item char *mon_thousands_sep
Similar to @code{thousands_sep}, but used for amounts of money.
@code{``''} in the C locale.

@item char *mon_grouping
Similar to @code{grouping}, but used for amounts of money.
@code{``''} in the C locale.

@item char *positive_sign
A string to flag positive amounts of money when formatting.
@code{``''} in the C locale.

@item char *negative_sign
A string to flag negative amounts of money when formatting.
@code{``''} in the C locale.

@item char int_frac_digits
The number of digits to display when formatting amounts of money to
international conventions.
@code{CHAR_MAX} (the largest number representable as a @code{char}) in
the C locale. 

@item char frac_digits
The number of digits to display when formatting amounts of money to
local conventions.
@code{CHAR_MAX} in the C locale. 

@item char p_cs_precedes
@code{1} indicates the local currency symbol is used before a
@emph{positive or zero} formatted amount of money; @code{0} indicates
the currency symbol is placed after the formatted number.
@code{CHAR_MAX} in the C locale. 

@item char p_sep_by_space
@code{1} indicates the local currency symbol must be separated from
@emph{positive or zero} numbers by a space; @code{0} indicates that it
is immediately adjacent to numbers.
@code{CHAR_MAX} in the C locale. 

@item char n_cs_precedes
@code{1} indicates the local currency symbol is used before a
@emph{negative} formatted amount of money; @code{0} indicates
the currency symbol is placed after the formatted number.
@code{CHAR_MAX} in the C locale. 

@item char n_sep_by_space
@code{1} indicates the local currency symbol must be separated from
@emph{negative} numbers by a space; @code{0} indicates that it
is immediately adjacent to numbers.
@code{CHAR_MAX} in the C locale. 

@item char p_sign_posn
Controls the position of the @emph{positive} sign for
numbers representing money.  @code{0} means parentheses surround the
number; @code{1} means the sign is placed before both the number and the
currency symbol; @code{2} means the sign is placed after both the number
and the currency symbol; @code{3} means the sign is placed just before
the currency symbol; and @code{4} means the sign is placed just after
the currency symbol.
@code{CHAR_MAX} in the C locale. 

@item char n_sign_posn
Controls the position of the @emph{negative} sign for numbers
representing money, using the same rules as @code{p_sign_posn}.
@code{CHAR_MAX} in the C locale. 
@end table

@menu
* setlocale::  Select or query locale
@end menu

@page
@include locale/locale.def
